---
title: "Clinical Variant Explorer Report"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: pdf_document
params:
  filtered_df: NULL
  filter_params: NULL
  plots: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(knitr)
library(dplyr)
```

## Summary

This report was generated by the Clinical Variant Explorer capsule.

**Variants after filtering:** `r nrow(params$filtered_df)`

## Active Filters

```{r filters}
fp <- params$filter_params

filter_summary <- data.frame(
  Filter = c("Chromosomes", "QUAL Range", "PASS Only", "MAF Range", "Genes", "Consequences", "Impacts"),
  Value = c(
    paste(fp$chr, collapse = ", "),
    paste(fp$qual_range, collapse = " - "),
    ifelse(fp$pass_only, "Yes", "No"),
    paste(fp$maf_range, collapse = " - "),
    ifelse(length(fp$genes) > 0, paste(fp$genes, collapse = ", "), "None"),
    ifelse(length(fp$consequences) > 0, paste(fp$consequences, collapse = ", "), "None"),
    ifelse(length(fp$impacts) > 0, paste(fp$impacts, collapse = ", "), "None")
  ),
  stringsAsFactors = FALSE
)

kable(filter_summary, caption = "Applied Filters")
```

## Top 20 Variants (by QUAL)

```{r top_variants}
top_variants <- params$filtered_df %>%
  arrange(desc(QUAL)) %>%
  head(20) %>%
  select(CHROM, POS, ID, REF, ALT, QUAL, Gene_Name, Effect, Impact)

kable(top_variants, caption = "Top Variants by QUAL Score")
```

## Variant Distribution by Impact

```{r impact_dist}
if ("Impact" %in% names(params$filtered_df)) {
  impact_counts <- params$filtered_df %>%
    count(Impact, name = "Count") %>%
    arrange(desc(Count))
  
  kable(impact_counts, caption = "Variants by Impact Level")
}
```

## Data Assets Used

- **VCF Source:** User-selected file from `/data/`
- **SnpEff Database:** GRCh38.105 (Data Asset: adb864a9-22f9-4c66-bee7-53e573ff10f0)
- **Reference Genome:** GRCh38 (Data Asset: b3db642d-6278-456b-8440-a8e06b16a08b)

---

*Report generated by Clinical Variant Explorer (Capsule ID: 2334e370-6f40-4343-b3de-10ef6e7dac64)*
